Identity Blockchain - Proof of Identity

### 2022-07-23 paper.tex
Statements to check registerP

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidKpUsed;

  function registerKp(
    uint hNinKid,
    uint hNinKidKp,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC
  ) public {

		//Setting public arguments
		uint[] memory inputValues = new uint[](2)
		inputValues[0] = hNinKid;
		inputValues[1] = hNinKidKp;

@@

    ninKidKpUsed[hNinKid] = hNinKidKp;
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item CA
\end{itemize}

>>>>

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidKpUsed;
	mapping(uint => bool) public isPerson;

  function registerKp(
    uint hNinKid,
    uint hNinKidKp,
		uint Kp,
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC
  ) public {

		//Setting public arguments
		uint[] memory inputValues = new uint[](3)
		inputValues[0] = hNinKid;
		inputValues[1] = hNinKidKp;
		inputValues[2] = Kp;

@@

    ninKidKpUsed[hNinKid] = hNinKidKp;
		isPerson[Kp]=true;
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}
\item[] \underline{Features}
\begin{itemize}
      \item[] \textbf{Sybil resistance} \\ $\khk$ is a unique public key bound to the Person on the \pbc{}. By design, the Person cannot have two valid $\khk$ keys at the same time.

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item Check first step (Register $\kid$) still valid
	\item Check hNinKid valid
	\item Check hNinKidKp valid
	\item Check Kp valid
	\item TODO: Kp invalidation!?
\end{itemize}
